---
title: "Fast Food Nutrition"
author: "Daniel Yang"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: true
    toc_depth: 4
    toc_float: true
runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
require(data.world)
knitr::opts_chunk$set(echo = TRUE)
```
  
## **R Session Info**  

```{r}
sessionInfo()
```

## **Connecting to data.world** 
```{r}
project <- "https://data.world/danielyangyiwen/fast-food-nutrition"
df <- data.world::query(data.world::qry_sql("SELECT * FROM Fastfood_Data"), dataset = project)
```

## **Calories for each restaurant (Boxplot)**
Here shows the vast array of ranges of calories for each restaurant and it's outliers. Denny's reigns supreme with the highest calories as a restaurant possibly indicating larger portions for each dish they serve.

```{r}
renderPlot({
boxplot(calories~restaurant, data = df, main = "Calories for Restaurant Items", xlab = "Restaurant", ylab = "Calories")
})
```

## **Calories from Fat vs Calories for each item (Scatterplot)**
Here is not a clear trend but there is a significant % of calories from fat with lower calorie items. This indicates that those types of foods/items are very fatty and possibly not good for a healthy diet/lifestyle. Generally food falls in the 40-60 calories from fat and ranging from 0 to 1500 calorie for a food item. In the end, Denny's seems to have large portions in terms of calories but is also heavy in proteins and other nutritional values that can be detrimental for one's health but may feed the soul meaning it tastes really good!

```{r}
renderPlot({
ggplot(df, aes(calories, cals_from_fat)) + geom_point(aes(colour = cut(cals_from_fat,c(-Inf,40,45,Inf))), size = 5, shape = 1) + 
  scale_color_manual(name = "cals_from_fat",values = c("(-Inf,40]" = "green",
                                                       "(40,45]" = "grey",
                                                       "(45, Inf]" = "red"),
                     labels = c("<= 40", "40 < cals_from_fat <= 45", "> 58"))
})
```

## **Nutrition Bar total values for meal types**
What is interesting that almost every single breakfast food for all the restaurants have a large amount of calories and cholesterol. Though breakfast foods do taste very good, it is most likely not recommended for a healthy diet/lifestyle. It beats the average calorie count for all the restaurants and the average calorie count for individual restaurant. Cholesterol is much the same.

```{r}
renderPlot({
ggplot(df, aes(x=restaurant, y=calories, fill=meal_type)) + geom_bar(stat = "identity", position=position_dodge())
})
```
```{r}
renderPlot({
ggplot(df, aes(x=restaurant, y=fiber_g, fill=meal_type)) + geom_bar(stat = "identity", position=position_dodge())
})
```
```{r}
renderPlot({
ggplot(df, aes(x=restaurant, y=cholesterol_mg, fill=meal_type)) + geom_bar(stat = "identity", position=position_dodge())
})
```
```{r}
renderPlot({
ggplot(df, aes(x=restaurant, y=protein_g, fill=meal_type)) + geom_bar(stat = "identity", position=position_dodge())
})
```
